# gridSVG + open_notebook()

The [blog posts about `gridSVG`](http://stattech.wordpress.fos.auckland.ac.nz/) offer some very fine examples.  I thought combining these with `rCharts` and `slidify` would provide a powerful combination.  Here are some quick experiments adding another layer of interactivity with `open_notebook()`.

## Example 1 - Filters in Statistical Graphics

```{r results='asis', cache = F, fig.keep='none'}
require(latticeExtra)
require(gridSVG)

#just for fun use one of the themes from latticeExtra
tp<-trellis.par.get()
trellis.par.set(theEconomist.theme())
xyplot(Sepal.Length + Sepal.Width ~ Petal.Length + Petal.Width | Species,
       data = iris, scales = "free", layout = c(2, 2),
       auto.key = list(x = .55, y = .7, corner = c(0, 0)))
blur <- filterEffect(feGaussianBlur(sd=2))
registerFilter("point-blur", blur)
grid.draw(filterGrob(textGrob(""), label="point-blur"))
legendSymbols <- grid.get("key.points", grep=TRUE, global=TRUE)
for (i in legendSymbols) {
  name <- i$name
  grid.garnish(name, 
               onclick=paste("highlight(", 
                             substr(name, nchar(name), nchar(name)),
                             ")", sep=""))
}

grid.export("")$svg
```

`grid.script` does not work in `open_notebook`, since the script gets parsed as markdown.  We could load scripts from a file or url like `grid.script` through something like

```
cat(
  "<script>",
  readLines("c:/myjavascriptfiles/highlight-blur.js"),
  </script>"
)
```
but I think the use case would favor writing the script as below.
```
function highlight(i) {
    for (row=1; row<3; row++) {
        for (col=1; col<3; col++) {
            for (j=1; j<5; j++) {
                var target = 
                    document.getElementById("plot_01.xyplot.points.group." 
                                            + j + ".panel." + 
                                            row + "." + col + ".1");
                if (i == j) {
                    target.setAttribute("filter", "none");            
                } else {
                    target.setAttribute("filter", "url(#point-blur.1)");
                }
            }
        }
    }
}
```


<script>
function highlight(i) {
    for (row=1; row<3; row++) {
        for (col=1; col<3; col++) {
            for (j=1; j<5; j++) {
                var target = 
                    document.getElementById("plot_01.xyplot.points.group." 
                                            + j + ".panel." + 
                                            row + "." + col + ".1");
                if (i == j) {
                    target.setAttribute("filter", "none");            
                } else {
                    target.setAttribute("filter", "url(#point-blur.1)");
                }
            }
        }
    }
}

</script>



## Example 2 - Gradient Fills in Statistical Graphics
```{r results='asis', cache = F, fig.keep='none',eval=FALSE}
xyplot(y ~ x, ylim=extendrange(c(y+delta, y-delta)), 
       pch=21, col="white", bg="black",
       panel=function(x, y, ...) {
           lrect(x-barwidth, y-delta, x+barwidth, y+delta,
                 border="transparent",
                 identifier="bar")
           panel.xyplot(x, y, ...)
       })
lg <- linearGradient(c("white", "black", "white"),
                     x0=.5, y0=0, x1=.5, y1=1)
registerGradientFill("lg", lg)
grid.gradientFill("bar.rect", label=rep("lg", 10), 
                  grep=TRUE, group=FALSE)
grid.export("")$svg
```

```{r results='asis', cache = F, fig.keep='none'}
trellis.par.set(ggplot2like())
plotdat <- aggregate(hp ~ gear + vs, data = mtcars, mean)
plotdat$gear <- factor(plotdat$gear)
plotdat$vs <- factor(plotdat$vs)
barchart(hp ~ gear, groups = vs, data = plotdat,
         xlab = "Number of Gears", ylab = "Mean Horsepower",
         auto.key = list(space = "right"), horizontal = FALSE)
fills <- c("#CCFFFF", "#FFCCFF")
val0pat <- pattern(gTree(children=gList(
                             rectGrob(gp=gpar(col=NA, fill=fills[1])),
                             linesGrob(gp=gpar(col="black")))),
                   width = unit(2, "mm"), height = unit(2, "mm"),
                   dev.width = 1, dev.height = 1)
val1pat <- pattern(gTree(children=gList(
                             rectGrob(gp=gpar(col=NA, fill=fills[2])),
                             filterGrob(circleGrob(r=.4, gp=gpar(lwd=5)), 
                                        filterEffect(feGaussianBlur(sd=10))))),
                   width = unit(2, "mm"), height = unit(2, "mm"),
                   dev.width = 1, dev.height = 1)
grid.export("")$svg
```

```{r results='asis', cache = F, fig.keep='none'}
require(quantmod)
japanReserves <- getSymbols(
  "TRESEGJPM052N",
  src = "FRED",
  auto.assign = FALSE
)

p1 <- xyplot(
  japanReserves,
  scales = list(y = list(rot = 1)),
  lattice.options = theEconomist.opts(),
  par.settings = theEconomist.theme(box="transparent"),
  main = "Japan Foreign Reserves excluding Gold"
)

p1
grid.export("")$svg
```